%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


% ___________________________________________________________________________
% CONFIGURATION

% Check awesome-cv.cls for all of the special functions.
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Builtin:
%   awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%   awesome-nephritis, awesome-concrete, awesome-darknight
% Custom:
%   \definecolor{awesome}{HTML}{CA63A8}
\colorlet{awesome}{awesome-red}

% Colors for text
\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{333333}
\definecolor{graytext}{HTML}{5D5D5D}
\definecolor{lighttext}{HTML}{999999}

% Set to false to disable section highlight
\setbool{acvSectionColorHighlight}{true}

% Set the social information separator to a textbar (|)
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


% ___________________________________________________________________________
% MACROS

% Custom commands for URLs without protocol prefixes
\newcommand*{\httpurl}[1]{\href{http://#1}{\nolinkurl{#1}}}
\newcommand*{\httpsurl}[1]{\href{https://#1}{\nolinkurl{#1}}}


% ___________________________________________________________________________
% PERSONAL INFORMATION

% Available options: circle|rectangle,edge/noedge,left/right
%\photo[rectangle,edge,right]{./profile}

\name{Yunkai}{Wang}
\position{Software Developer{\enskip\cdotp\enskip}Software Engineer}
\address{Ottawa, ON}

\mobile{+1 (613) 890-6018}
\email{yunkaiwang1996@gmail.com}
\github{yunkaiwang}
\linkedin{yunkaiwang}

% Supported but unused:
%\homepage{URL}
%\gitlab{gitlab-id}
%\stackoverflow{SO-id}{SO-name}
%\twitter{@twit}
%\skype{skype-id}
%\reddit{reddit-id}
%\extrainfo{extra informations}

% \quote{``Write programs that do one thing and do it well. Write programs to work together."}


% ___________________________________________________________________________
% CONTENT

\recipient
  {Company Recruitment Team}
  {<Company address>}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for <job title>}
% How the letter is opened
\letteropening{Dear <recruiter name/hiring manager>,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


\begin{document}

% Print the header with above personal informations
% The argument changes alignment (C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments (<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  %{\today}
  {}
  {Yunkai Wang~~~·~~~Cover Letter}
  {}  
%{\thepage}

\makelettertitle

% Resume sections are independent files.
\begin{cvletter}

\lettersection{About Me}
I am currently enrolled as a Master's student at Carleton. My anticipated graduation date is June 2021.
I have an outstanding academic performance at school, both as an undergraduate student and a
graduate student. I have received the Entrance Scholarship from Carleton in full amount, and I was
awarded the Senate Medal when I finished my Bachelor's study. I have completed a total of
four co-op work terms at three different companies with hands-on experience with many large-scale
projects. I developed a keen interest in advanced data structures and algorithms, and I can effectively
apply them in real applications for performance improvement. I am also skilled in object-oriented
programming and deployment and development of web applications; I launched a lost-and-found
mobile app using Express and React Native, and I have also integrated BigBlueButton with open
source platforms like Zimbra and Open Edx. I am always passionate to learn cutting-edge technologies
and apply them in projects and systems. I have refined my strengths in project management,
technical troubleshooting, and problem resolution through my years of professional experience.


\lettersection{Why <company>?}


\lettersection{Why Me?}
With my wide-ranging technical skills, superior capacity to tackle time-sensitive projects, and proven
ability to deliver best-in-class customer service, I am confident that I will exceed your expectations
from my first day on the job.

\end{cvletter}

\makeletterclosing

\end{document}
