\cvsection{Experience}
\begin{cventries}

\cventry
{Blindside Network Inc.}
{Open Source Integration Developer}
{Ottawa, ON}
{May. 2018 - Aug. 2018}
{\begin{cvitems}
    \item {Installed and integrated BigBlueButton with open-source platforms to manage entire activities at one spot and improve online learning process.}
    \item {Implemented BigBlueButton API libraries using both Java and Python for formatting the API requests and parsing the responses.}
    \item {Developed a zimlet for Zimbra users to freely use BigBlutButton; extended Zimbra server by adding both HTTP and SOAP request handler for meeting administration and receive callbacks from BigBlueButton server.}
    \item {Deployed an XBlock using XBlock SDK for integrating Open Edx with BigBlueButton; supported features including join meeting and BigBlueButton server configuration.}
\end{cvitems}}

\cventry
{Carleton University}
{Programmer}
{Ottawa, ON}
{May. 2017 - Dec. 2017}
{\begin{cvitems}
    \item {Established and launched an automated diagnostic test generation application for elementary arithmetic skills improvement; developed a decoding application for analyzing the test result and reporting user's deficient skills; documented a user manual for the application.}
    \item {Implemented multiple code generation methods for generating the best test template.}
    \item {Applied web server for computing disjunct matrix based on the given input, along with a monitor for overseeing the healthy status of the server.}
\end{cvitems}}

\cventry
{Espial Group Inc.}
{Java Developer}
{Ottawa, ON}
{Sep. 2016 - Dec. 2016}
{\begin{cvitems}
    \item {Collaborated in an Agile team; participated in the full software development life cycle.}
    \item {Configured virtual labs on AWS to offer easier access to the MSP platform for global customers and increase the lab availability for other developers and teams; migrated and configured the entire MSP platform on EC2 instances.}
    \item {Maintained and upgraded existing containerized applications; executed automated tests for app efficiency enhancement.}
    \item {Founded JESB, an internal team management tool for monitoring teams' statistics.}
\end{cvitems}}

\cventry
{Carleton University}
{Teaching Assistant}
{Ottawa, ON}
{Sep. 2015 - Apr. 2021}
{\begin{cvitems}
    \item {Offered operational and administrative support to professors; delivered a range of teaching and assessment activities including tutorials directed towards the successful delivery of subjects; provided effective timely and appropriate feedback to students to support their learning.}
    \item {Prepared and lessoned two lectures for the Theory of Computation course.}
    \item {Managed nine different undergraduate level courses and supervised over five hundred students.}
\end{cvitems}}

\cventry
{Carleton University}
{Research Assistant}
{Ottawa, ON}
{May. 2020 - Apr. 2021}
{\begin{cvitems}
    \item {Worked under the supervision of Prosenjit Bose and Ahmad Biniaz on uncovering simplified algorithms for piercing disks in the plane.}
\end{cvitems}}

\end{cventries}
