\cvsection{Projects}
\begin{cventries}

\cventry
{\textnormal{\httpsurl{github.com/dsp-uga/elizabeth}}}
{Elizabeth: Scalable malware detection}
{UGA}
{2018}
{\begin{cvitems}
    \item {A Spark based approach to the \href{https://www.kaggle.com/c/malware-classification/}{Microsoft Malware Classification Challenge}.}
    \item {Developed in a team of three over two weeks as a project in UGA's Data Science Practicum.}
    \item {Achieved the best accuracy in the class.}
    \item {I implemented the preprocess pipeline and naive Bayes analysis.}
    \item {I also implemented the build and deployment scripts for Google Cloud Dataproc.}
\end{cvitems}}

\cventry
{\textnormal{\httpsurl{github.com/cbarrick/evo}}}
{Evo: Parallel genetic algorithms in Go}
{UGA}
{2016}
{\begin{cvitems}
    \item {Support for fine-grain parallelism in arbitrary topologies.}
\end{cvitems}}

\cventry
{\textnormal{\httpsurl{github.com/cbarrick/Rw-Prolog}}}
{Rw-Prolog: An equational logic programming language}
{UGA}
{2015}
{\begin{cvitems}
    \item {Extends Prolog's unification semantics with support for conditional term-rewriting.}
    \item {Implemented as a meta-interpreter in Prolog.}
    \item {Developed a regular expression engine using the language.}
\end{cvitems}}

\cventry
{\textnormal{\httpsurl{github.com/cbarrick/plum}}}
{Plum: A logical agent for the board game \textit{Clue}}
{UGA}
{2014}
{\begin{cvitems}
    \item {Communicates with a human operator in natural language (English).}
    \item {Models knowledge as a constraint satisfaction problem.}
    \item {Uses path-finding and probability estimates to make decisions.}
    \item {Super-human performance.}
\end{cvitems}}

%---------------------------------------------------------
\end{cventries}
