\cvsection{Projects}
\begin{cventries}

\cventry
{\textnormal{\httpsurl{github.com/Jasonjys/retrieve}}}
{Retrieve}
{Carleton U.}
{2017}
{\begin{cvitems}
    \item {\textbf{Technologies}: React Native, Express, Node.js, Firebase, EC2 instance, S3 bucket}
    \item {A free-to-use lost-and-found mobile app deployed on iOS; supported user registration or log in through Facebook identity provider; permitted users create posts or query posts using keywords or locations.}
    \item {Created and applied chat functionality; allowed sending images and locations to other users and stored figures in S3 bucket.}
    \item {Constructed a web server on EC2 instance for handling query and chat requests; cached query results in local memory to achive low latency and increase server availability; automatically generate .}
\end{cvitems}}

\cventry
{\textnormal{\httpsurl{github.com/yunkaiwang/TFTPFileTransferSystem}}}
{TFTP File Transfer System}
{Carleton U.}
{2018}
{\begin{cvitems}
    \item {\textbf{Technologies}: Java, Socket programming}
    \item {Implemented a connection-less file transfer system based on the TFTP specialization.}
    \item {Supported traditional file manipulation commands used in Linux in the terminal based user interface.}
\end{cvitems}}

\cventry
{\textnormal{Espial's internal tool}}
{JESB, Jira to ElasticSearch Bridge}
{Espial}
{2016}
{\begin{cvitems}
    \item {\textbf{Technologies}: Elastic Search, Kibana, Node.js, Quality Automated Test Framework}
    \item {Founded an internal team management application for monitoring teams' statistics; designed automated tests for app efficiency enhancement.}
\end{cvitems}}

\cventry
{\textnormal{\httpsurl{https://github.com/yunkaiwang/DouDiZhuAI}}}
{Landlord poker game AI}
{Carleton}
{2019}
{\begin{cvitems}
    \item {\textbf{Technologies}: Swift, Perfect, Best-reply Search}
    \item {Presented an innovative method of building a game search algorithm based on Best-reply Search for the landlord poker game.}
    \item {Constructed an mobile app on iOS that allows users play against AI players powered by the proposed algorithm.}
    \item {Launched a web server using Perfect to transfer the computational expensive tasks to the server.}
\end{cvitems}}

%\cventry
%{\textnormal{\httpsurl{github.com/yunkaiwang/SmartSnake} \hspace{5pt}/\hspace{5pt} \httpsurl{github.com/yunkaiwang/Smart2048}}}
%{Smart Snake / Smart 2048}
%{Carleton U.}
%{2018}
%{\begin{cvitems}
%    \item {\textbf{Technologies}: Processing, Neural Network, Genetic Algorithm}
%    \item {Established an AI technique to play simple board games and analyzed the limitation of the technique.}
%    \item {Evolved neural network with genetic algorithm and served randomly initialized parameters as the initial population.}
%\end{cvitems}}

\cventry
{\textnormal{\httpsurl{github.com/yunkaiwang/comp4107/tree/master/project}}}
{Judging a book by its title}
{Carleton U.}
{2018}
{\begin{cvitems}
    \item {\textbf{Technologies}: Scikit-learn, Tensorflow, Keras, Numpy, Matplotlib, Python}
    \item {Applied convolutional neural networks for categorizing books based on their titles; acquired 66\% validation accuracy using pre-trained GloVe embeddings; investigated the limitations of MLP models for NLP-related tasks.}
\end{cvitems}}




%---------------------------------------------------------
\end{cventries}
